### 2016-11-16 R/ITHIM.Rmd
Created Dose-Response Figure and tweaked Figure 1 from Methods Paper

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
install.packages(c("knitr","ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

@@

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(45, 120, length.out = 5)
muNonTravelVec <- c(1, 5, 10)
DTotal <- data.frame()

@@

p <- ggplot(DTotal, aes(x = at,y = -DALYs/1e3, colour = quants))
p + stat_smooth( method = loess) + geom_point() + theme_bw() + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + scale_x_continuous(name="Active Transport (minutes/week) (Referent Group)") + facet_grid( . ~ muNonTravel) + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8))

@@

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
#install.packages(c("knitr","ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

@@

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(37.5, 120, length.out = 10)
muNonTravelVec <- c(1, 10, 25)
DTotal <- data.frame()

@@

DTotal <- within(DTotal, muNonTravel <- factor(muNonTravel, levels = as.character(muNonTravelVec), labels = c("low","medium","high")))
DTotal <- subset(DTotal, quants == "percentiles")

p <- ggplot(DTotal, aes(x = at, y = -DALYs/1e3, colour = muNonTravel))
p + geom_line() + geom_point() + theme_bw() + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + scale_x_continuous(name="Active Transport (minutes/week) (Referent Group)")  + scale_colour_discrete(name="Baseline Activity") #+ theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8))

@@

```{r doseresponse, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
RR1vec <- unique(unlist(createActiveTransportRRs()))
lapply(createActiveTransportRRs(),function(x) lapply(x, function(x) unique(c(x))))
#~~~~~~~~~~~~~~~~~~~~~~~
# Manual bullshit!
#~~~~~~~~~~~~~~~~~~~~~~~
RR1vec <- RR1vec[RR1vec != 1]
names(RR1vec) <- c("BreastCancer","ColonCancer.M","ColonCancer.F", "CVD", "Dementia", "Depression.young", "Depression.old", "Diabetes")

RRx <- function(x, RR1, k) exp(log(RR1)*x^k)
x <- seq(0,25,0.1)
RRmat <- outer(x, RR1vec, RRx, k = 0.5)
rownames(RRmat) <- x
D <- melt(RRmat)
names(D) <- c("x","disease","RR")

p <- ggplot(D, aes(x = x, y = RR, colour = disease))
p + geom_line()  + theme_bw() + scale_y_continuous(name="Relative Risk") + scale_x_continuous(name="Physical Activity (MET-hrs./week)")
```
